---
title: "fourSynergy - Postprocessing"
format: 
    html: 
        embed-resources: true
params:
    config: "x"
    vp: "y"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=15)

library(GenomicRanges)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(forcats)
library(stringr)
library(reshape2)
library(slider)
library(tidyr)
library(yaml)
```

```{r config, include=FALSE}
# config <- read_yaml('../Datasets/Geeven_sox////info.yaml')
# config <- read_yaml('../Datasets/Modrek_SOX2////info.yaml')
#config <- read_yaml('../Datasets/Takeda_promoter_siGATA2/////info.yaml')

config <- read_yaml(file = params$config)
```

```{r, viewpoint, include=FALSE}
#vi.in <- '../Datasets/Geeven_sox/viewpoint.bed'
#vi.in <- '../Datasets/Modrek_SOX2/viewpoint.bed'
#vi.in <- '../Datasets//Takeda_promoter_siGATA2/viewpoint.bed'

# vi <- read.csv(params$vp, sep = '\t')
# 
# 
# vi <-  vi[vi$name != 'VP',]
# vi$name <- factor('known')
# colnames(vi) <- c('seqnames', 'start', 'end', 'nReads', 'tool')
# vi$tool <- factor('known')
# vi$seqnames <- as.factor(vi$seqnames)

vp <- data.frame(seqnames = paste0('chr', config$VPchr),
                 start = config$VPpos-1000,
                 end = config$VPpos+1000, 
                 tool = factor('VP'))

message(getwd())
message(config)
res.path <- paste0('../results/', config$author, '/')
```

```{r, include=FALSE}
create_dir_if_not_exist <- function(dir_path) {
    if (!file.exists(dir_path)) {
        message('Builing dirs')
        dir.create(dir_path)
    }
}

create_dir_if_not_exist(paste0(res.path, 'sia'))
```

```{r, include=FALSE}
source('./ensemble_functions.R')

addStartToPeakC <- function(peakc.obj, basic4c.vfl, sample.name){
    sample <- deparse(substitute(peakc.obj))
    peak.df <- data.frame(seqnames = character(), start = integer(), 
                          end = integer(),
                          nReads = integer(), tool = factor())
    
    if (!is.null(peakc.obj$peak) & length(peakc.obj$peak) > 0){
        peaks <- peakc.obj$peak %>% 
            data.frame(seqnames = paste0('chr', config$VPchr), start = ., end = .) %>% 
            makeGRangesFromDataFrame()
        ov <- findOverlaps(peaks, basic4c.vfl)
        hit.frag <- unique(basic4c.vfl[subjectHits(ov),])
        
        
        # Bring peakC to strandard format
        if (length(hit.frag) > 0){
            print('rows in peakc')
            hit.frag$tool <- sample.name
            
            peak.df <- hit.frag %>%
                as.data.frame() %>% 
                dplyr::select(seqnames, start, end, tool) %>%
                mutate(nReads = -1 )
        }
        return(peak.df) 
    }
}

addStartToPeakCSig <- function(peakc.collect, basic4c.vfl, sample.name){
    #sample <- deparse(substitute(peakc.collect))
    # Check if hits fragment
    peaks <- peakc.collect$dbr %>%  
        mutate(seqnames = paste0('chr', config$VPchr), start = end) %>%  
        makeGRangesFromDataFrame(keep.extra.columns = TRUE)
    ov <- findOverlaps(peaks, basic4c.vfl)
    hit.frag <- basic4c.vfl[subjectHits(ov),]
    hit.frag$significance <- mcols(peaks[queryHits(ov),])$significance
    
    # remove double entries
    hit.frag <- unique(hit.frag)
    peak.df <- as.data.frame(hit.frag)
    
    # Bring peakC to strandard format
    if (nrow(peak.df) > 0){
        peak.df <- peak.df %>% 
            mutate(nReads = -1) %>% 
            mutate(tool = sample.name) %>%
            dplyr::select(seqnames, start, end, nReads, tool, significance)
    }
    return(peak.df)
}
```

# Load ouput data from

-   r3C seq
-   peakC
-   fourSig
-   r4cker

```{r data, echo=FALSE}
# Read r3C seq
if (!is.null(config$control)){
    tryCatch({
        try(r3c_1_obj <- readRDS(paste0(res.path, 'r3cseq/r3Cseq_obj.rds')))
        r3c_2000_obj <- readRDS(paste0(res.path, 'r3cseq/r3Cseq_2000_obj.rds'))
        r3c_5000_obj <- readRDS(paste0(res.path, 'r3cseq/r3Cseq_5000_obj.rds'))
        r3c_10000_obj <- readRDS(paste0(res.path, 'r3cseq/r3Cseq_10000_obj.rds'))},
        error = function(e){
            message('Found no r3c rds files!')
        })
} else {
    tryCatch({
        for (f in list.files(paste0(res.path, 'r3cseq'), '*.rds', full.names = T)) {
            sample <- basename(f) %>% 
                str_extract(., '(.*)(_sorted_r3Cseq_)(\\d+)(_obj.rds)', c(3, 1))
            assign(paste0('rds.r3c_', sample[1], '.', sample[2]), readRDS(f))
        }
    }, error = function(e){
        message('Found no r3c rds files!')
    })
}

# Read fourSig
tryCatch({
    for (w in list.files(paste0(res.path, 'fourSig/'),
                         '*_w_fourSigit_\\d+.rds',
                         full.names = T)) {
        window <- str_extract(w, "(?<=fourSigit_)\\d+")
        sample <- gsub('_w_fourSigit_\\d+.rds', '', basename(w))
        assign(paste0('rds.foursigit_', window, '.', sample), 
               readRDS(gsub('_w', '', w)))
    }
}, error = function(e){
    message('Found no fourSig rds files!')
})


# Read peakC
tryCatch({
    files <- list.files(paste0(res.path, 'peakC'), 
                        '(0.01|0.05|0.1)\\.rds', full.names = T)
    for (f in files) {  
        sample <- gsub('.rds', '', basename(f)) %>%  
            gsub('(peakC_\\d+)_', '\\1.', .) %>%
            gsub("_(?=[^_]*$)", ".", ., perl = TRUE) %>% gsub('peakC', 'peakc', .)
        assign(paste0('rds.', sample), readRDS(f))
        
    }
}, error = function(e){
    message('Found no peakC rds files!')
})

```

# Read Virtual fragment library (vfl) (Basic4Cseq)

```{r read.vfl, echo=FALSE}
paste0('../results/vfl/', config$organism, '_', 
                              config$RESeq[1], '_', config$RESeq[2], '_',
                              config$readLength, '_VFL.csv')
# Read Basic data
basic.frag <- read.csv(paste0('../results/vfl/', config$organism, '_',
                              config$RESeq[1], '_', config$RESeq[2], '_',
                              config$readLength, '_VFL.csv'), sep = '\t')

basic.frag.chr <- basic.frag[basic.frag$chromosomeName ==
                                 paste0('chr', config$VPchr),]
colnames(basic.frag.chr)[1] <- 'seqnames'
basic.frag.chr.gr <- makeGRangesFromDataFrame(basic.frag.chr)

# Map VP on fragments
overlap <- findOverlaps(makeGRangesFromDataFrame(vp), basic.frag.chr.gr,
                        type = 'any')

# Get the indices of the fragments hit by at least one peak
fragment_hits <- subjectHits(overlap)

# Extract the fragments hit
vp.gr <- basic.frag.chr.gr[fragment_hits]
```

Read Basic4Cseq files

```{r basicvis, echo=FALSE}
basic.frag <- read.csv(list.files(paste0(res.path, 'basic4cseq/'), 
                                  '*_frags.csv', full.names = T)[1], sep = '\t')
print(list.files(paste0(res.path, 'basic4cseq/'), 
                 '*_frags.csv', full.names = T)[1])
colnames(basic.frag)[4] <- paste0('reads_', 
                                  gsub('_frags.csv', '', list.files(paste0(
                                      res.path, 'basic4cseq/'), '*_frags.csv')[1]))
for (b in list.files(paste0(res.path, 'basic4cseq/'), 
                     '*_frags.csv', full.names = T)[-1]){
    sample <- gsub('_frags.csv', '', basename(b))
    basic.frag.tmp <- read.csv(b, sep = '\t')
    colnames(basic.frag.tmp)[4] <- paste0('reads_', sample)
    basic.frag <- merge(basic.frag, basic.frag.tmp, all = T)
}

ctrl <- basic.frag[grep(pattern = config$condition, colnames(basic.frag))]
basic.frag <- basic.frag %>%
    mutate(condition = rowMeans(dplyr::select(., contains(match = paste0('reads_',config$condition), ignore.case = FALSE)))) %>%
    mutate(control = rowMeans(dplyr::select(., contains(match = paste0('reads_',config$control), ignore.case = FALSE)))) 

# Create dummy.gr to use this if tool called no sias
dummy.gr <- makeGRangesFromDataFrame(data.frame(
    seqnames=paste0('chr', config$VPchr),start=0,end=0, nReads = -1, 
    significance = 0), keep.extra.columns = T)
```

Define nearbait area

```{r nearbait, echo=FALSE}
overlap <- findOverlaps(vp.gr, basic.frag.chr.gr, type = 'any')

# Get the indices of the fragments hit by at least one peak
vp.index <- subjectHits(overlap)

# Define area of interest
# Make sure that indices are available
lower.bound <- ifelse((vp.index[1] -1500) > 0, (vp.index[1] -1500), 0)
upper.bound <- ifelse((vp.index[length(vp.index)] + 1500 - length(vp.index)) <=
                          length(basic.frag.chr.gr), 
                      (vp.index[length(vp.index)] + 1500 - length(vp.index)), 
                      length(basic.frag.chr.gr))
nearbait.area <- basic.frag.chr.gr[lower.bound:upper.bound,]

if (vp.index[1] -1500 < 0){
    fill <- rep(dummy.gr,abs(vp.index[1] -1500 -1)) 
    nearbait.area.out <- c(fill, nearbait.area)
    names(nearbait.area.out) <- seq(1, length(nearbait.area.out))
} else {
    nearbait.area.out <- nearbait.area
}

nearbait.area.out %>% 
    as.data.frame() %>%
    dplyr::select(seqnames, start, end) %>%
    write.table(.,paste0(res.path, 'nearbait_area.bed'),  quote = F, 
                row.names = F, sep = '\t')
```

# Transform data into sia format

```{r, echo=FALSE}
# Create list where sia granges are stored
list.sia.all <- GRangesList()
list.sia.all[['VP']] <- vp.gr
list.sia.all <- list.sia.all[!grepl("seqinfo", names(list.sia.all))]
```

## r3Cseq

```{r r3cseq, echo=FALSE}
tryCatch({
    # If Control is involved replicates are collapsed in r3c object
    if (!is.null(config$control)){
        for (r3c in c('r3c_2000_obj', 'r3c_5000_obj', 'r3c_10000_obj')){
            # Check if r3c objcet was written
            if (exists(r3c)){
                
                # Iterate over different window sizes
                for (f in setdiff(ls(pattern = '^r3c_'), lsf.str())){
                    # gr <- get(paste0('r3c_', n, '_obj'))@expInteractionRegions
                    # Iterate over condition and control
                    for (cond in c('condition', 'control')){
                        gr <- slot(get(f), ifelse(cond == 'condition', 
                                                  'expInteractionRegions', 
                                                  'contrInteractionRegions'))
                        
                        # Check if there are peaks if not insert dummy.gr
                        if (length(gr) == 0) gr <- dummy.gr
                        
                        # Extract significant interactions on VP chromosome
                        mcols(gr)$significance <- 0
                        gr$significance[gr$q.value < 0.1] <- 1  # TODO change in r3c
                        gr$significance[gr$q.value < 0.05] <- 2
                        gr$significance[gr$q.value < 0.01] <- 3
                        
                        gr <- gr[seqnames(gr) == paste0('chr', config$VPchr) & 
                                     gr$p.value < 0.05]  # TODO change later
                        
                        # remove 0 significance
                        gr <- gr[gr$significance > 0]
                        
                        # Map on fragments (is already fragment based but on r3c fragments) 
                        overlap <- findOverlaps(gr, basic.frag.chr.gr, type = 'any')
                        
                        # Get the indices of the fragments hit by at least one peak
                        fragment_hits <- subjectHits(overlap)
                        
                        # Extract the fragments hit
                        hit_fragments <- basic.frag.chr.gr[fragment_hits]
                        
                        if (length(hit_fragments) == 0){
                            hit_fragments <- dummy.gr
                            hit_fragments$tool <- paste0('rep.r3c_',
                                                         str_split_fixed(f, '_', 3)[2], '.', 
                                                         config[cond])
                        } else {
                            hit_fragments$tool <- paste0('rep.r3c_', 
                                                         str_split_fixed(f, '_', 3)[2], '.', 
                                                         config[cond])
                            hit_fragments$significance <- gr[queryHits(overlap)]$significance
                            hit_fragments$q.value <- gr[queryHits(overlap)]$q.value
                            
                        }
                        list.sia.all[[paste0('rep.r3c_', str_split_fixed(f, '_', 3)[2], '.', 
                                             config[cond])]] <- hit_fragments
                    }
                }
                
                # Write dummies if no r3c_obj was written
            } else {
                warning('\nNo r3c_obj has been found. Please check this!\n')
                r3c.tool <- r3c %>% gsub('_obj', '', .)
                # cond dummy
                gr <- dummy.gr
                gr$tool <- paste0('rep.', r3c.tool, '.', config$condition)
                list.sia.all[[paste0('rep.', r3c.tool, '.', config$condition)]] <- gr
                
                # control dummy
                gr <- dummy.gr
                gr$tool <- paste0('rep.', r3c.tool, '.', config$control)
                list.sia.all[[paste0('rep.', r3c.tool, '.', config$control)]] <- gr
            }
        }
    }
    # Reads single rds files if no control is involved
    else {
        # Extract object and iterate over them
        for (f in setdiff(ls(pattern = '^rds.r3c'), lsf.str())) {
            fi <- get(f)
            sample <- gsub('rds.r3c.', '', gsub('_sorted', '', basename(f)))
            
            # Extract significant interactions
            if (length(fi@expInteractionRegions) == 0){
                r3c.tmp <- dummy.gr
            } else {
                r3c.tmp <- fi@expInteractionRegions %>%
                    as.data.frame() %>%
                    filter(seqnames == paste0('chr', config$VPchr)) %>%
                    filter(p.value < 0.05) %>%
                    dplyr::select(seqnames, start, end, nReads, q.value) %>%
                    mutate(tool = paste0('single.r3c_', sample)) %>%
                    makeGRangesFromDataFrame(keep.extra.columns = T)
                
                mcols(r3c.tmp)$significance <- 0
                r3c.tmp$significance[r3c.tmp$q.value < 0.1] <- 1  # TODO change in r3c
                r3c.tmp$significance[r3c.tmp$q.value] <- 2
                r3c.tmp$significance[r3c.tmp$q.value < 0.01] <- 3
                
                overlap <- findOverlaps(r3c.tmp, basic.frag.chr.gr, type = 'any')
                
                # Get the indices of the fragments hit by at least one peak
                fragment_hits <- subjectHits(overlap)
                
                # Extract the fragments hit
                hit_fragments <- basic.frag.chr.gr[fragment_hits]
                
                if (length(hit_fragments) == 0){
                    hit_fragments <- dummy.gr
                    hit_fragments$tool <-  paste0('single.r3c.', sample) 
                } else {
                    hit_fragments$tool <-  paste0('single.r3c.', sample) 
                    hit_fragments$significance <- 0
                }
            }
            
            list.sia.all[[paste0('single.r3c_', sample)]] <- r3c.tmp
        }
    }
})
plotConsens.grl(consens.df = list.sia.all[grepl('(single|rep).r3c_*', names(list.sia.all))],  xlim = c(config$VPpos-1000000, config$VPpos+1000000))
```

## fourSig

```{r fourSig, echo=FALSE}
# Iterate over foursig rds objects and bring them to sia format
fs.samples <- paste0(rep(paste0("rds.foursigit_", c(1,3,5,11), ".", 
                    config$condition, "_"), each = max(config$conditionRep)), 
         config$conditionRep) 
    
if (!is.null(config$control))fs.samples <- c(fs.samples, paste0(rep(paste0("rds.foursigit_", c(1,3,5,11), ".", 
                  config$control, "_"), each = max(config$controlRep)), config$controlRep))
    
try(for (f in fs.samples){ 
    
    # Extract sample name
    sample <- gsub('rds.', 'single.', f)
    
    if (exists(f)){
        #  Bring foursig output to sia format
        tmp.gr <- get(f) %>% 
            dplyr::mutate(tool = sample) %>%
            dplyr::mutate(chr = as.factor(paste0('chr', chr))) %>%
            dplyr::mutate(reads = as.numeric(reads)) %>%
            dplyr::rename(seqnames = chr) %>%
            dplyr::rename(nReads = reads) %>%
            dplyr::rename(significance = category) %>%
            mutate(significance = recode(significance, 
                                         `3` = 1, 
                                         `1` = 3)) %>%
            makeGRangesFromDataFrame(keep.extra.columns = T)
        
        if (startsWith(sample, "single.foursig_1.")){
            # Map onto fragments
            # TODO only if frag is 0 
            overlap <- findOverlaps(tmp.gr, basic.frag.chr.gr, type = 'any')
            
            # Get the indices of the fragments hit by at least one peak
            fragment_hits <- subjectHits(overlap)
            
            # Extract the fragments hit
            hit_fragments <- basic.frag.chr.gr[fragment_hits]
            if (length(hit_fragments) == 0){
                hit_fragments <- dummy.gr
                hit_fragments$tool <- sample
                mcols$significance <- 0
            } else {
                hit_fragments$tool <- sample
                mcols(hit_fragments)$significance <- tmp.gr[queryHits(overlap)]$significance
            }
            # Collect sia object in list
            list.sia.all[[sample]] <- hit_fragments
        } else {
            list.sia.all[[sample]] <- tmp.gr
        }
    } else {
        message(paste0('No ', f, ' found. Dummy'))
        hit_fragments <- dummy.gr
        hit_fragments$tool <- sample
        hit_fragments$significance <- 0
        list.sia.all[[sample]] <- hit_fragments
    }
})

# Remove rds foursig objects from env
rm(list = ls(pattern = "^rds\\.foursig"))
plotConsens.grl(consens.df = list.sia.all[grepl('single.foursig.*', names(list.sia.all))],  xlim = c(config$VPpos-1000000, config$VPpos+1000000))
```


## PeakC
Add significance information 

```{r peakcsig, echo=FALSE}
if (is.null(config$control)) {
  pc <- c('condition')
} else {
  pc <- c('condition', 'control')
}
		

# Iterate over peakC results and process them
try(for(cond in pc){
        for (w in c(1, 11, 21, 31, 51, 101)){
            p <- setdiff(ls(pattern = paste0('^rds.peakc_',w,'\\.', 
                                             config[cond],'.*_alphaFDR')), lsf.str())
            
            # Collect peaks called with different sig levels in a list
            x <-lapply(p, function(x) get(x)$peak)
            res <- rev(lapply(length(p):1, function(n){
                diff <- setdiff(x[[n]], unlist(x[n-1]))
                result <- if (length(diff) == 0) {
                    ""
                } else {
                    diff
                }
            }))
            
            # Name entries according to the significance level were the opeaks were called
            names(res) <-  as.numeric(str_match(basename(p), '0\\.\\d+'))
            df <- data.frame(
                FDR_level = rep(names(res), sapply(res, length)), end = unlist(res)) %>% 
                mutate(significance = recode(FDR_level,
                                             '0.01' = 3,
                                             '0.05' = 2,
                                             '0.1' = 1,
                                             '0.25' = 0,
                                             '0.5' = 0)) %>% 
                filter(end != "", significance > 0)
            
            # Bring the peaks to peakc format to add peak starts
            peak.esc.collect <- list()
            peak.esc.collect$dbr <- df
            peak.esc.collect$peak <- unique(unlist(res))
            
            # Create sample name for collected peaks              
            sample <- str_extract(p[1], 'peakc_\\d+\\.[^_]+(_[^_]*)*$') %>% 
                gsub('peakc', 'rep.peakcSig', .) %>%
                gsub("(_[^_]+)$", "", .)
            
            # Add start
            tmp <- addStartToPeakCSig(peakc.collect = peak.esc.collect,
                                      basic4c.vfl = basic.frag.chr.gr, sample.name = sample) %>% 
                mutate(tool = sample) 
            
            # If peaks are found
            if (nrow(tmp) > 0){
                tmp.gr <- makeGRangesFromDataFrame(tmp, keep.extra.columns = T)
                tmp.gr<-  tmp.gr[tmp.gr$significance > 0] 
                
                # Collect sia object in list
                list.sia.all[[sample]] <- tmp.gr
            } else {
                message('No sias found by peakc, add dummy gr.')
                dummy.gr.p <- dummy.gr
                dummy.gr.p$tool <- sample
                list.sia.all[[sample]] <- dummy.gr.p
            }}
    }
)

try(plotConsens.grl(
    consens.df = list.sia.all[grepl('rep.peakcSig|VP', names(list.sia.all) )],
    xlim = c(config$VPpos-1000000, config$VPpos+1000000)))
```

# 4C-ker

```{r, echo=FALSE}
# If no sia found r4cker writes out empty bed file -> dummy.gr
r4ckers <- list.files(paste0(res.path, 'r4cker/out'), 
                      paste0(gsub( '\\+', '\\\\+', config$author),
                             '_(',config$condition,'|', config$control, ')',
                             '_(nearbait|cis)_highinter.*.bed'), full.names = T)

# Iterate over r4cker bed files
try(for (i in seq_along(r4ckers)){
    sample <- paste0('rep.r4cker_', 
                     basename(r4ckers[i]) %>%
                         str_extract(paste0('(', gsub('+', '\\+', config$author, fixed = TRUE), ')', 
                                            '_(.*)_(cis|nearbait)_(highinter|lowinter).bed$'), c(3, 2)) %>% 
                         paste(., collapse = '.'))
    
    # If files has lines read it
    file_path <- r4ckers[i]
    
    # Get the file size once
    file_size <- file.size(file_path)
    
    # Check if the file size is NA
    if ((file_size == 0)) {
        print("File is empty")
        r <- dummy.gr
        r$tool <- sample
        list.sia.all[[sample]] <- r 
    } else {
        # Attempt to read the file
        r <- read.delim(file_path, sep = '', header = FALSE)
        colnames(r) <- c('seqnames', 'start', 'end')
        r$nReads <- -1  
        r$significance <- 3
        
        # Map onto nearbait
        overlap <- findOverlaps(makeGRangesFromDataFrame(r), nearbait.area, 
                                type ='any')
        fragment_hits <- subjectHits(overlap)
        
        # Extract the fragments hit
        hit_fragments <- nearbait.area[fragment_hits]
        
        if (length(hit_fragments) == 0){
            hit_fragments <- dummy.gr
        }
        
        hit_fragments$significance <- r[queryHits(overlap),]$significance  
        hit_fragments$tool <- sample
        
        # Collect sia object in list
        list.sia.all[[sample]] <- hit_fragments
    }
})

try(plotConsens.grl(
    consens.df = list.sia.all[grepl('rep.r4cker*|VP', names(list.sia.all) )],
    xlim = c(config$VPpos-1000000, config$VPpos+1000000)))
```

# Summarize replicates
# Collapse Replicates

```{r collpase.rep, echo=FALSE}
#' Extract all elements from grangeslist from individial ("single") samples
#' These are grouped by tools and then by treatment and than collapsed via
#' majority vote
samples <- names(list.sia.all)[startsWith(names(list.sia.all), 'single')]
tool <- unique(str_split_i(samples, "\\.", i = 2))

for(t in tool){
    print(t)
    # Extract condition and ctrl sias of selected tool
    # Extract all samples of one tool 
    single.tmp.tool <- list.sia.all[startsWith(names(list.sia.all), 
                                               paste0('single.', t, '.'))]
    
    # Extract only treatment info without replicate
    single.tmp.split.tool <- split(single.tmp.tool, sub("_[^_]*$", "", 
                                                        names(single.tmp.tool)))
    
    # Iterate over condition and control, calculate majority vote over replicates
    try(
        for (i in rev(names(single.tmp.split.tool))) {
            min <- ceiling(length(config$conditionRep)/2)  
            mv <- getMajorityVote.grl(intervalls = single.tmp.split.tool[[i]], 
                                      greater.than = min)
            mv$tool <- gsub('single', 'rep', i)
            print(gsub('single', 'rep', i))
            list.sia.all[[gsub('single', 'rep', i)]] <- mv
            rm(mv)
        })
}
```

# Add significance information to fourSig if necessary
should not be done on rep.foursig since here fragments are summarized

```{r, warning=FALSE, echo=FALSE}
# Iterate over replcates
# only on r3c if single condition TODO test
samples <- names(list.sia.all)[grepl('single.(foursig|r3c)',names(list.sia.all))]  
tool <- unique(str_split_i(samples, "\\.", i = 2))

for(t in tool){
    print(t)
    # Extract condition and ctrl sias of selected tool
    # Extract all samples of one tool 
    single.tmp.tool <- list.sia.all[startsWith(names(list.sia.all), 
                                               paste0('single.', t, '.'))]
    
    # Extract treatment and replicate info
    single.tmp.split.tool <- split(single.tmp.tool, sub("_[^_]*$", "", 
                                                        names(single.tmp.tool)))
    
    # Iterate over condition and control, get significance information from replicates
    try(
        for (cond in names(single.tmp.split.tool)) {
            # Extract replicates for current condition
            cond.tmp <- str_extract(cond, '(?<=\\.)[^\\.]+$')
            single.tmp.rep <- as.numeric(str_extract(names(single.tmp.tool)[grepl(cond.tmp, names(single.tmp.tool))], '(?<=\\_)[^\\_]+$'))
            
            # Iterate over replicates and collect significance information in sia rep slot
            for (i in single.tmp.rep) {
                # New significance_[rep] column
                mcols(list.sia.all[[gsub('single', 'rep',cond)]])[[paste0('significance_', i)]] <- NA
                
                # Lookup significance in corresponding single.[tool]_[rep] and add it
                sig.lookup <-  list.sia.all[[paste0(cond, '_', i)]]
                ov <- findOverlaps(list.sia.all[[gsub('single', 'rep',cond)]], sig.lookup)
                sig.lookup[subjectHits(ov)]
                mcols(list.sia.all[[gsub('single', 'rep',cond)]][queryHits(ov)])[ paste0('significance_', i)] <-   sig.lookup[subjectHits(ov)]$significance
            }    
            
            # Summarize significance over all replicates
            reps.df <- as.data.frame(mcols(list.sia.all[[gsub('single', 'rep',cond)]])) %>% dplyr::select(paste0('significance_', single.tmp.rep))
            
            # Create significance vector
            significance <- rep(NA, nrow(reps.df))
            
            # Apply function to each row to create the significance vector
            significance <- apply(reps.df, 1, function(row) {
                # Convert row to numeric and drop NAs
                row <- row[!is.na(row)]
                table_values <- sort(table(row), decreasing = T)  # Create a frequency table
                max_count <- max(table_values)  # Get the maximum count
                
                # If valze occurs in more than the half of the reps -> return it
                if (max_count >= floor(ncol(reps.df) / 2 + 1)) {
                    return(as.numeric(names(table_values)[1]))  # Return the value if meets criteria
                    
                    # If mixed values but more than in the half of replicates no NA
                } else if (length(table_values) >= floor(ncol(reps.df) / 2 + 1)){
                    return(floor(mean(row)))
                } else {
                    return(0)
                }
            }
            )
            mcols(list.sia.all[[gsub('single', 'rep',cond)]])['significance'] <- significance
        })
}
plotConsens.grl(consens.df = list.sia.all,  xlim = c(config$VPpos-1000000, 
                                                     config$VPpos+1000000))
```

# Crete sia files

```{r sia, echo=FALSE}
smoothFillSiaNB <- function(sia = GRanges(), nearbait.area,
                            lookup.size = integer(), config = data.frame(), 
                            step = 1, outfile = character(), vp.gr = GRanges()){
    out.name <- gsub(paste0(sub(".*\\.", "", sia$tool[1]), '$'), 
                     ifelse(sub(".*\\.", "", sia$tool[1]) == config$condition, 
                            'condition', 'control'), 
                     gsub('rep', '', paste0('../results/', config$author, 
                                            '/sia/', config$author, 
                                            gsub('\\.', '_', sia$tool[1]))))

    # Add significance information to virtual fragment library (vfl)
    # Map fragments onto vfl
    ov <- findOverlaps(nearbait.area, sia)
    
    # Check if fragments getting lost
    unique(subjectHits(ov)) %>% length() == length(sia)
    
    # Add significance information from sias
    nearbait.area$significance <- 0
    nearbait.area[queryHits(ov)]$significance <- sia[subjectHits(ov)]$significance
    nearbait.area %>%
        as.data.frame() %>%
        dplyr::select(seqnames, start, end, significance) %>%
        # filter(significance > 0) #%>%
        write.table(paste0(out.name, '_nearbait.bed'), quote = F, row.names = F, 
                    sep = '\t')
}
```

```{r, echo=FALSE}
sel <- names(list.sia.all)[grepl('rep.(peakcSig_\\d|foursig|r4cker|r3c_\\d)', names(list.sia.all))]
process_sia <- function(s) {
    tryCatch({
        smoothFillSiaNB(sia = list.sia.all[[s]], nearbait.area = nearbait.area.out, config = config, vp.gr = vp.gr)
    }, error = function(e) {
        message("Error processing ", s, ": ", e$message)
    }, warning = function(w) {
        message("Warning in ", s, ": ", w$message)
    })
}

# Process each selection
try(sapply(sel, process_sia))

# Plotting with tryCatch
tryCatch({
    plotConsens.grl(list.sia.all[names(list.sia.all)[grepl('rep.(r3c(flat)*|peakcSig(flat)*|foursig|r4cker)|VP',
                                                           names(list.sia.all))]], xlim = c(config$VPpos - 500000, config$VPpos + 500000))
}, error = function(e) {
    message("Error in plotting: ", e$message)
})
```

```{r, eval=FALSE}
file.create(paste0(res.path, 'sia/finished.txt'))
```
